{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-03 Paper/main.tex

	\paragraph{Monomial Basis}
	Due to the high collinearity of these basis{(\color{orange} How about stressing the higher order? Are they already highly correlated at lower orders?)}, simulations were conducted up until the sixth monomial basis, excluding the first one since this just represents a constant. For reasons outlined in {\color{green} Link chapter}, they are suited for the smooth function $f_1$ and show a better performance than bsplines for this coefficient function, but show the weakest performance for the coefficient function $f_2$. For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratios. This weakness is especially pronounced in the setup $f_2,Y_1$; for the high noise setup, $f_2, Y_2$ this weakness is still visible, but less strongly pronounced.

	\paragraph{Bspline Basis}
	Simulations with bspline basis functions were possible from 5 to 18, since from 18 onwards the simulations were running into problems concerning {\color{green} what happend here exactly?}
The smooth function $f_1$ requires only 5(4) Bspline basis functions, for the high(low)-signal-to-noise ratio to obtain the best fit for the bspline basis, which performs the worst for $f_1$. For $f_2$, 11(6) bspline basis functions are needed for the high(low) signal-to-noise ratios. For $f_2$, the bspline basis functions outperform the monomial basis, but come second to the fourier basis.

>>>>

	\paragraph{Monomial Basis}
	Due to the high collinearity of these basis{(\color{orange} How about stressing the higher order? Are they already highly correlated at lower orders?)}, simulations were conducted up until the sixth monomial basis, excluding the first one since this just represents a constant. For reasons outlined in {\color{green} Link chapter}, they seem suited for $f_1$ and show a better performance than bsplines for this coefficient function, but show the weakest performance for the coefficient function $f_2$. For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratios. This weakness is especially pronounced in the setup $f_2,Y_1$; for the high noise setup, $f_2, Y_2$ this weakness is still visible, but less strongly pronounced.

	\paragraph{Bspline Basis}
	Simulations with bspline basis functions were possible from 5 to 18, since from 18 onwards the simulations were running into problems concerning {\color{green} what happend here exactly?}
The smooth function $f_1$ requires only 5(4) Bspline basis functions, for the high(low) signal-to-noise ratio to obtain the best fit for the bspline basis, which performs the worst for $f_1$. For $f_2$, 11(6) bspline basis functions are needed for the high(low) signal-to-noise ratios. For $f_2$, the bspline basis functions outperform the monomial basis, but come second to the fourier basis.
